Transfer Learning in Visual and Relational Reasoning

### 2020-02-08 Transfer_Learning/cvpr_2nd_submission/samnet.tex
added t subscript to h^r and h^a

\noindent\textbf{Memory Update Unit.}
The unit first determines the memory location where an object could be added:
\[ \vec{w}_t = \doreplace \cdot \rhead_t + \doadd \cdot \whead_{t-1} \]
Above, $\vec{w}_t$ denotes the pseudo-attention vector that represents the ``location'' where the memory update should happen.
$\vec{w}_t$ sums up to at most 1 and can be zero, indicating in this case there is no need adding a new object nor replacing an existing object.
We then update the memory accordingly:
\[ \vec{M}_t = \vec{M}_{t-1} \odot (\vec{J} - \vec{w}_t  \otimes \mathbf{1}) + \vec{w}_t  \otimes \vec{vo}_t,\]
where $\vec{vo}_t$ denotes the object returned by the visual retrieval unit.
Here $\vec{J}$ denotes the all ones matrix, $\odot$ denotes the Hadamard product and $\otimes$ denotes the Kronecker product.
Note that the memory is unchanged in the case where $\vec{w}_t = 0$, i.e., $\vec{M}_t = \vec{M}_{t-1}$.
We finally update the write head so that it points to the succeeding address if an object was added to memory or otherwise stay the same.
Let $\whead'_{t-1}$ denote the circular shift to the right of $\whead_{t-1}$ which corresponds to the soft version of the head update.
Then:
\[ \whead_t = \doadd \cdot \whead'_{t-1} + (1-\doadd) \cdot \whead_{t-1} \]

>>>>

\noindent\textbf{Memory Update Unit.}
The unit first determines the memory location where an object could be added:
\[ \vec{w}_t = \doreplace_t \cdot \rhead_t + \doadd_t \cdot \whead_{t-1} \]
Above, $\vec{w}_t$ denotes the pseudo-attention vector that represents the ``location'' where the memory update should happen.
$\vec{w}_t$ sums up to at most 1 and can be zero, indicating in this case there is no need adding a new object nor replacing an existing object.
We then update the memory accordingly:
\[ \vec{M}_t = \vec{M}_{t-1} \odot (\vec{J} - \vec{w}_t  \otimes \mathbf{1}) + \vec{w}_t  \otimes \vec{vo}_t,\]
where $\vec{vo}_t$ denotes the object returned by the visual retrieval unit.
Here $\vec{J}$ denotes the all ones matrix, $\odot$ denotes the Hadamard product and $\otimes$ denotes the Kronecker product.
Note that the memory is unchanged in the case where $\vec{w}_t = 0$, i.e., $\vec{M}_t = \vec{M}_{t-1}$.
We finally update the write head so that it points to the succeeding address if an object was added to memory or otherwise stay the same.
Let $\whead'_{t-1}$ denote the circular shift to the right of $\whead_{t-1}$ which corresponds to the soft version of the head update.
Then:
\[ \whead_t = \doadd_t \cdot \whead'_{t-1} + (1-\doadd_t) \cdot \whead_{t-1} \]
